---
eval: false
toc: true
---

### 1. Install R & Quarto

You need both: 
 
- Install [{{< fa brands r-project >}}](https://CRAN.R-project.org/)
- Install [Quarto](https://quarto.org/)

We also recommend working with an IDE that has good support for R, Quarto, and Shiny.

[RStudio](https://posit.co/products/open-source/rstudio/) is great, and we also like [VSCode](https://code.visualstudio.com/) and [Positron](https://github.com/posit-dev/positron).

### 2. Install the `surveydown` R package

You can install `surveydown` from CRAN in your R console:

```{r}
install.packages("surveydown")
```

or you can install the development version from [GitHub](https://github.com/surveydown-dev/surveydown):

```{r}
# install.packages("pak")
pak::pak("surveydown-dev/surveydown")
```

Load the package with:

```{r}
library(surveydown)
```

You can also check which version you have installed:

```{r}
surveydown::sd_version()
```

### 3. Install the `sdApps` R package

You can install the development version (not on CRAN yet) of `sdApps` from [GitHub](https://github.com/surveydown-dev/sdApps):

```{r}
# install.packages("pak")
pak::pak('surveydown-dev/sdApps)
```
